\Huge Conferences in the Era of Expensive Carbon

### 2019-06-27 main.tex
Clarification
de-Macronized the second proposal

SIGPLAN has also explored how to mitigate a conference's {\COtwoE} emissions by
purchasing \emph{carbon offsets}~\cite{CarbonOFfsetReport}.
%
A carbon offset is sold by a vendor who uses the raised funds to finance an
activity that permanently avoids emitting some amount of greenhouse gases.
The veracity and permanence of this {\COtwoE} emission avoidance is certified by
a watchdog organization. (Typically, planting trees is not a certifiable
activity, since it's hard to guarantee the trees won't be cut down, but
installing methane capture devices on landfill sites or buying
fuel-efficient stoves to replace open-fire cooking in poor communities can
be.)
%
Many organizations, including companies such as Google, Dell, Microsoft,
General Motors, Delta Airlines, Lyft, and Expedia, numerous universities,
and some academic societies, now buy carbon offsets in order to reduce their
net footprint. ACM conferences can do the same, and the purchases can be
included in the public accounting we are proposing.  In fact, ACM recently
decided that conferences could offer attendees the option to pay for an
offset during registration; the conference then uses the designated funds to
purchase the offset from a qualified vendor.  Some conferences are also
experimenting with corporate sponsorship of bulk offsets for the whole
conference.\footnote{We acknowledge that carbon offsets are a 
  controversial 
  tool~\cite{anderson2012inconvenient,
  carbon-offsets-are-not-our-get-out-jail-free-card}.  Besides issues with
  verifiability and permanence, some observers worry that---especially at
  their current artificially low cost---they will encourage complacency,
  leading organizations to postpone making the difficult changes that will
  be required to sustainably decarbonize society.  We believe that offsets
  should be considered as a useful short-term expedient, to be considered in
  parallel with, not instead of, more difficult cutting.}
% \mwh{Should
% we mention the FCRC numbers here? 45 out of 2,700 used {\COtwoE} offsets}
% That's getting too much down into the details, I think -- also, these
% numbers reflect a hastily organized, preliminary version of what we really
% want to do.

@@

\begin{figure}[t]
\centering
\includegraphics[width=6in]{SIGPLAN-confs2.png}
\includegraphics[width=6in]{ParticipantsOriginAll2.png}
% \includegraphics[width=6in]{Distances.png}
\caption{Top: Carbon footprint per participant for travel to recent SIGPLAN
  conferences\iflater\bcp{Get better file from the other paper, or get
    better version of this one from Crista.}\fi.  (The smallest dot (ICFP
  14, in Gothenburg, Sweden) represents .9 tons of {\COtwoE} per participant; the
  largest dot (ICFP 16, in Nara Japan) represents 1.94 tons per
  participant.) Bottom: Breakdown of continent-of-origin for participants in
  each conference.
% Bottom: Distances traveled by participants, one way, in Km; middle dashed
% line is the median travel distance. 
}
\label{fig:confs}
\end{figure}

@@

What should ACM do with the funds collected from this surcharge?  One can
imagine many good uses, including carbon offsetting, defraying the costs of
virtualizing conferences (livestreaming, etc.), and supporting ``green''
computing research. As an example of the last, ACM could help fund a major
cross-cutting research initiative specifically aimed at understanding how to
best replace or approximate the socializing and networking aspects of
conferences in a virtual setting?

>>>>

SIGPLAN has also explored how to mitigate a conference's {\COtwoE} emissions by
purchasing \emph{carbon offsets}~\cite{CarbonOFfsetReport}.
%
A carbon offset is sold by a vendor who uses the raised funds to finance an
activity that permanently avoids emitting some amount of greenhouse gases.
The veracity and permanence of this {\COtwoE} emission avoidance is certified by
a watchdog organization. (Typically, planting trees is not a certifiable
activity, since it's hard to guarantee the trees won't be cut down, but
installing methane capture devices on landfill sites or buying
fuel-efficient stoves to replace open-fire cooking in poor communities can
be.)
%
Many organizations, including companies such as Google, Dell, Microsoft,
General Motors, Delta Airlines, Lyft, and Expedia, numerous universities,
and some academic societies, now buy carbon offsets in order to reduce their
net footprint. ACM conferences can do the same, and the purchases can be
included in the public accounting we are proposing.  In fact, ACM recently
decided that conferences could offer attendees the option to pay for an
offset during registration; the conference then uses the designated funds to
purchase the offset from a qualified vendor.  Some conferences are also
experimenting with corporate sponsorship of bulk offsets for the whole
conference.  
%
(We acknowledge that carbon offsets are a 
  controversial 
  tool~\cite{anderson2012inconvenient,
  carbon-offsets-are-not-our-get-out-jail-free-card}.  Besides issues with
  verifiability and permanence, some observers worry that---especially at
  their current artificially low cost---they will encourage complacency,
  leading organizations to postpone making the difficult changes that will
  be required to sustainably decarbonize society.  We believe that offsets
  should be considered as a useful short-term expedient, to be considered in
  parallel with, not instead of, more difficult cutting.)
% \mwh{Should
% we mention the FCRC numbers here? 45 out of 2,700 used {\COtwoE} offsets}
% That's getting too much down into the details, I think -- also, these
% numbers reflect a hastily organized, preliminary version of what we really
% want to do.

@@

\begin{figure}[t]
\centering
\includegraphics[width=6in]{SIGPLAN-confs2.png}
\includegraphics[width=6in]{ParticipantsOriginAll2.png}
% \includegraphics[width=6in]{Distances.png}
\caption{Top: Carbon footprint per participant for travel to recent SIGPLAN
  conferences\iflater\bcp{Get better file from the other paper, or get
    better version of this one from Crista.}\fi.  (The smallest dot (ICFP
  14, in Gothenburg, Sweden) represents .9 tons of {\COtwoE} per participant; the
  largest dot (ICFP 16, in Nara Japan) represents 1.94 tons per
  participant.) Bottom: Breakdown of continent-of-origin for participants in
  each conference.  Colored bars represent percentages of participants whose
  home city is in each continent.
% Bottom: Distances traveled by participants, one way, in Km; middle dashed
% line is the median travel distance. 
}
\label{fig:confs}
\end{figure}

@@

What should ACM do with the funds collected from this surcharge?  One can
imagine many good uses, including carbon offsetting, defraying the costs of
virtualizing conferences (livestreaming, etc.), and supporting ``green''
computing research. As an example of the last, ACM could help fund a 
cross-cutting research initiative specifically aimed at understanding how to
best replace or approximate the socializing and networking aspects of
conferences in a virtual setting.  But before any of this, the first concern
should be to find ways of {\em reducing} the finanial burden of such a
surcharge on those who may be disproportionately affected by it---students
without grant support, participants from developing areas, etc.  That is,
wealthier participants should subsidize the carbon footprints of less
fortunate ones.
